\documentclass{report}

\begin{document}

\begin{titlepage}
\centering{\LARGE\bfseries North South University}
\vspace{4\baselineskip}

{\large Project Proposal}
\vspace{4.5\baselineskip}

{\Large Topic: CAR AUCTION MANAGEMENT   }
	\vspace{2.5\baselineskip}
	
	{\Large Course Faculty:Nadeem Ahmed }
	\vspace{0.5\baselineskip}
	
	
{\Large Lab Instructor: Nazmul Alam Dipto }
	\vspace{4.5\baselineskip}


{\Large Database System Lab     \vspace{0.5\baselineskip}
		
		CSE311L \vspace{0.5\baselineskip}
		
		Section:5 \vspace{0.5\baselineskip}
		
		Semester: Summer 2021 \vspace{0.5\baselineskip} }
		\vspace{4.5\baselineskip}
		
{\Large Student name and Id:     \vspace{0.5\baselineskip}
		
		Group 10 \vspace{0.5\baselineskip}
		}
		
{\Large Jahid Akand Nahid (1813142642)\vspace{0.5\baselineskip}
		
		Faiza Akter (1912308042) \vspace{0.5\baselineskip}
		
		Marion Moon (1911973642)\vspace{0.5\baselineskip}
		}
		
\end{titlepage}	

\section{Introduction}
With the development of our economy people often hunt for comfort life. As there is enormous amount of traffic jam and the both bus root and service are unorganized in our country so there is nothing convenient then a privet car for movement. People always prefer a used well conditions featureful car then a new less featured car. Budget preference for a same product always varies with people to people. Here comes our project to help people to find their best deal within their budget.
\section{Objectives}

•	To easily access sign in.

•	Simple outlook.

•	Sell used car.

•	Bid according to budget for buy car.

•	Car information.

•	Notification of bus arrival


\section{Target Customers}

•	Financially stable people: people who are willing to buy or sells used car and want to bid for their next deal.

•	Rent-car service company: They are our potential consumers. A huge number of rent car company willing 
\section{Value Proposition}
This website will reduce the bothering and time of going to a bus stop and constantly ask them for booking a seat in bus. It will also reduce the cost of keeping a manager to keep track of the information. Bus owner will be notified for updating the papers which will reduce the chance of being late and hence, saving the penalty money.

\section{Web Application Feature and description}
The web page will open with the simple beautiful view. Anyone with the internet can access this page. This page will show the below option and on top there will be a log in page directory if people willing to take service they have to sign-up: 
  
•	New assign car.

•	Best deal.

•	All cars information.

•	Sort by name and price

On top there will be log in or sign-up consumer. They will be able to add their company to the database and see their progress. Once a bus Owner has created a profile, he/she can:



•	See the information of their car and paper work.

•	Place their bid, and hide bid.

•	Just able to see the last highest bid.

•	Sort by price.

•	Upload their used car for sell and set their minimum set price.

•	weekly and monthly ranking of highest bid and most wanted bus.

•	Feedback of their service.

•	The current status of their bid.


\section{Tools and Resources}

	HTML
	
	Xampp
	
	JavaScript
	
	MySQL
	
	PHP
	
	Web server
	
	API for SMS

\section{Challenges}
One of the biggest problems is to collect the data of all models’ cars and their information. To collect data there will be huge cost. And a huge server. verifying data is also a big challenge. Gaining people’s trust is also a challenging fact.

\end{document}


