\documentclass{report}

\begin{document}

\begin{titlepage}
\centering{\LARGE\bfseries North South University}
\vspace{4\baselineskip}

{\large Project Proposal}
\vspace{4.5\baselineskip}

{\Large Topic: CAR AUCTION MANAGEMENT   }
	\vspace{2.5\baselineskip}
	
	{\Large Course Faculty:Nadeem Ahmed }
	\vspace{0.5\baselineskip}
	
	
{\Large Lab Instructor: Nazmul Alam Dipto }
	\vspace{4.5\baselineskip}


{\Large Database System Lab     \vspace{0.5\baselineskip}
		
		CSE311L \vspace{0.5\baselineskip}
		
		Section:5 \vspace{0.5\baselineskip}
		
		Semester: Summer 2021 \vspace{0.5\baselineskip} }
		\vspace{4.5\baselineskip}
		
{\Large Student name and Id:     \vspace{0.5\baselineskip}
		
		Group 10 \vspace{0.5\baselineskip}
		}
		
{\Large Faiza Akter (1912308042) \vspace{0.5\baselineskip}
		
		Marion Moon (1911973642)\vspace{0.5\baselineskip}
		}
		
\end{titlepage}	

\section*{Introduction}
With the development of our economy people often hunt for comfort life. As there is enormous amount of traffic jam and the both bus root and service are unorganized in our country so there is nothing convenient then a privet car for movement. People always prefer a used well conditions featureful car then a new less featured car. Budget preference for a same product always varies with people to people. Here comes our project to help people to find their best deal within their budget.

\section*{About Car Hunt BD}

In the world of civilization we make the proper way to make it happen to move faster then other, we Focus on innovation car, on that note we start out journey 1989 from a small.garage, we then bye old car and sell it to other,. But as a company we have to move with digital world, every tiny things people can buy from internet so why people had to search thousands of newspaper to find where any auction happen, keeping that in mind we build a fully mordern, organised online auction and selling system, if you are a international user don't you worries we have sever international billing methods too so lets go!



We are a company that willing to make a paradise for car enthusiasts. When its about to buy a car people usually don't have much idea or information to get to know about their desire also there is muck lack info about the pricing of a car. We mainatain our server twice a week. So its quite easy for a person to know about pricing. keeping in mind about the budget and desire of people we build online car auction system and selling system, we start our journey as a small automobile company back in 1989, now we want to take our business one step ahead we digitalise our whole system. We have different billing method so this auction opportunity is for everyone all over the world.


\section*{Purpose and Benefits of Car Auction Management System:}


\subsection*{• Purpose of Car Auction Management System:}


Regardless of their source, vehicles are sent to auction with the main purpose to be sold quickly and hassle-free, and this usually happens at prices that dealers can easily recoup with a small profit from a resale.

\subsection*{• Benefits of Car Auction Management System:}

\textbf{Benefits of AuctionCarz project:}

\begin{enumerate}
\item 100 percent original cars: We have seen thousands of fraud cases that make our worries     about used cars more difficult. Auctions purchased cars are 100 percent original because these are select by us. The provided information about the vehicle uploaded by the authentic company and car inspection man.
\item Exact Meter Reading:  Most dealers change the meter reading for getting high amounts from consumers. But there is no chance of this mishap in car auction purchases. The exact meter reading mentioned with vehicle information.
\item No Fake Auction Sheets: The availability of the auction sheet report makes your car value high in the customer’s mind. Dealers take benefit from this and provide a fake auction sheet to customers. But the purchase of an auction house car verifiable even after 10 years. When you bought a car from auctions they provide an auction sheet report that is original.
\item Check Accident Cars: The price of accidental cars is lower than in excellent condition cars. Even the vehicle is a minor accident, it will not be considered in the grade. Cars are available live and you can see the damaged part of the car. Pictures and details of all cars mention auctions cars.
\item Choose from a lot of Inventory Options: There are a lot of our dream car options available. You can find the best one for yourself by searching for your demanding cars. More than 250 auction houses are located in Japan and almost all are provided online vehicle selling options. Many inventory options are available in which all types of vehicles available truck, SUVs, sedan, crossover, hatchback, and many small cars.
\item All Range of Colors Availability: Everyone has their mindset of car colors. The most common and popular colors are white, pearl white, black, red, and silver. But auctions show you a vast range of color variety. The availability of colors in inventory is very large you can choose any of your favorite colors to live.
\item Wide Range Car Features to Choose as you Want: The demand for high-class features in cars increased with time spending. As technology is evolving advanced entertaining and safety features in cars increased. Today a single small car offers more than 100+ features to entertain consumers. A wide range of features availability increased the interest of people in Japanese cars. All Japanese cars offer advanced features and day by day it’s increasing.
\item Check Denting Pending Before Buying:  You can check deeply your car before buying it. Car auction not only offers service online. you can physically check the car before buy if you are in Japan. You can also check it online because of clear pictures of vehicles available on the auction website for customers.
\item Save From Fraud: The fear of fraud less in auction house purchased the car. You can buy your car by yourself its means you have all information about your car. If you have all related information about your vehicle there is no chance of fraud.

\end{enumerate}

\section*{Front End Plan}


1. Main page

2. Login page

3. Signup page

4. Explore page

5. Most Popular page

6. Live Auction page

7. Auction Time And Date page

8. About Us page

9.Top Bidding Page


\section*{Back End Development}

\subsection*{• Account Creating, Password Recover:} 

\subsubsection*{a. Sign up form, verification by mobile or email.}

\subsubsection*{b. Login}

\subsubsection*{c. Forgot Password}


\subsection*{• Profile Management:} 


\subsubsection*{a. Seller Profile}

\subsubsection*{b. Buyer Profile}

\subsubsection*{c. Details of previous Auctions}

\subsubsection*{d. Others}


\subsection*{• Searching facility:} 

• Searching cars

\section*{Tools and technologies:}

	HTML
	
	Xampp
	
	JavaScript
	
	MySQL
	
	PHP
	
	Web server
	
	API for SMS

\section*{Conclusion:}

An online based Car Auction Management System is a technological tool used to buy and sell cars online. Our online based car auction System will decrease the hassle of physical presence for a auction. They will be able to bid online, know the timing of bidding, will be able to view top bidding. Customers will be able to see their previous bidding detail, can manage their own profile. 

\end{document}


